\TitleText

### 2019-11-06 presentation-B/4_simulation.tex
Fix presentation typos

\Frame {Real Valued Representation}
{
\I To solve the convex optimization, we use Python package CVXPY.

\I Since it doesn't allow complex variables, we represent complex number by real part and imarinary parts.

@@

\I For matrices, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a, \NC -b \NR
\NC b, \NC a \NR
\stopTheMatrix \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (1/3)}
{
\I Given are \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m{\g > 0}.
Let \m {\T {\V {y}}} be the real representation of \m {\V {y}}, and \m {\T {\M {P}}} that of \m {\M {P}}.

@@

\I Similarly, for \m {i = N_H^2, N_H^2 +1, \ldots, 2N_H^2 -1},
\Disp{
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix, \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\V {y}},
\Q \V {c}_i
= \V {0},
\Q d_i
= \g \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (3/3)}
{
\I Now, run the Second Order Cone Programming:
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}
\MC \IP {\V {t}, \V {x}'} \NR
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
\NC \MC i 
=0, 1, \ldots, 2N_H^2 -1 \NR
\stopcases \NR
}
\I Extract channel response as real vector:
\Disp {
\NC \Hat{\V {g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\V {x}} \DB {0 : 2N_H^2-1}} \NR
}
\I Convert back from Angular domain and output:
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Bound of log of error norm:
\Disp {
\NC \h_{\Ss{th}}
\eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
}
\I Log absolute / relative error:
\Disp {
\NC \h_{\Ss{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}} \NR
%
\NC \h_{\Ss{rel}}
=\NC \F {\h_{\Ss{abs}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 32, 48}
\I Antennae number of analog stage \m {N_R = \RB {\log N_H}^2}
\I Antennae number of digital stage \m {N_Y = \log N_H}
\I Analog beamformer quantization grid: \m {16}
\I Number of paths \m {L =4}
\I How many noise standard deviation tried: \m {12}
\I Number of repetition of each data point: \m {16}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{

>>>>

\Frame {Real Valued Representation}
{
\I To solve the convex optimization, we use Python package CVXPY.
To save complexity, we represent a complex number by its real- and imarinary-parts.

@@

\I For matrices, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a, \NC -b \NR
\NC b, \NC a \NR
\stopTheMatrix \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (1/3)}
{
\I Given are \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m{\g _{\Ss {DS}} > 0}.
Let \m {\T {\V {y}}} and \m {\T {\M {P}}} respectively be their real representation.

@@

\I Similarly, for \m {i = N_H^2, N_H^2 +1, \ldots, 2N_H^2 -1},
\Disp{
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix, \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\V {y}},
\Q \V {c}_i
= \V {0},
\Q d_i
= \g _{\Ss {DS}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (3/3)}
{
\I Now, run the Second Order Cone Programming:
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}
\MC \IP {\V {t}, \V {x}'} \NR
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
\NC \MC i 
=0, 1, \ldots, 2N_H^2 -1 \NR
\stopcases \NR
%
\NC \Hat{\V {g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\V {x}} _{\SB {0 : 2N_H^2-1}}} \NR
%
\NC \Hat {\M {H}}
\LA \NC \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Bound of log of error norm:
\Disp {
\NC \h_{\Ss{th}}
\eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
}
\I Log absolute / relative error:
\Disp {
\NC \h_{\Ss{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}} \NR
%
\NC \h_{\Ss{rel}}
=\NC \F {\h_{\Ss{abs}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 32, 48}
\I Antennae number of analog stage \m {N_R = \RB {\log N_H}^2}
\I Antennae number of digital stage \m {N_Y = \log N_H}
\I Analog beamformer quantization grid: \m {16}
\I Number of paths \m {L =4}
\I How many noise standard deviation tried: \m {12}
\I Number of repetition of each data point: \m {16}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{

### 2019-11-06 presentation-B/5_conclusion.tex
Fix presentation typos

\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).

\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.

\I We bound the expected square error and , in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}, and discussed with the big \m {\MC{O}} of the successful probability
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Investigate the reason of high complexity and reduce it

\I Run for bigger values of \m {N_H}, \m {N_Y}, and \m{L} if possible

\I Maybe try the real case and use existent code for DS

\I More literature review on OMP and other methods
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References}
{
{\tfx
\I E. Candès and J. Romberg, \It {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved from \Tt {www.acm.caltech.edu/l1magic/downloads/l1magic.pdf}, 2005.

>>>>

\Frame {Conclusion}
{
\I We propose a feasible method to estimate MIMO mm-Wave channel \m {\M {H}} by exploiting its sparsity, and employing Dantzig Selector (DS).

\I We modified DS for present setting, for the almost-sparse condition in the angular domain, with respect to the effective beamformer \m {\M {P}} in our setting, and concerning complex vectors.

\I We bound the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the big \m {\MC{O}} of the successful probability
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Investigate the reason of high complexity and reduce it.

\I Run for bigger values of \m {N_H}, \m {N_Y}, and \m{L} if possible.

\I Maybe try the real case and use existent code for DS.

\I More literature review on other methods.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References}
{
{\tfx
\I E. Candès and J. Romberg, \It {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved from \Tt {www.acm.caltech.edu/l1magic/downloads/l1magic.pdf}, 2005.
